Normal States Training for High Accuracy Event Detection

### 2016-06-14 paper/main.tex
add tikz files

\section{Method}
\textbf{User profile.} User usually describes herself or himself by a piece of short text on microblog platform.
This short text can be a continuous string or an array of hash tags, e.g., "\textit{Co-founder of Twitter, Medium, and now Co-founder and CEO of Askjelly.com}" of Biz Stone or "\textit{\#Cloud}, \textit{\#YARN}" of @hadoopchina.
Though it's easy to estimate Biz Stone's interests by his self-description text, it's not always capable of doing so because some users' are very short.
To overcome this limitation, we define \textbf{user profile} \(\bm{p_u}\) as combining user \(u\)'s self-description text with the texts provided by \(u\)'s followings. 
Taking Biz Stone as an example, he follows 696 accounts, in which there are 60 founders, 27 CEOs, 21 Google related, and 9 medium related accounts, etc. 
This example demonstrates that user profile \(p_u\) can be augmented by gathering the followings' information.

@@

\begin{equation}
\label{eq:wikiPrior}
\begin{aligned}
\tau_{kv}=
\left\{ \begin{aligned}
W \frac{n_{kv}}{\sum_{v\in S_{kv}}n_{kv}} &,v\in S_{k} \\
0&,v \notin S_{k}\\
\end{aligned}\right.
\end{aligned}
\end{equation}

@@

As shown in Figure \ref{fig: windowsBurstyWordGraph} below, we will one area, a hot word of the time window and hot words between to diagram.
Hot words set \(\ mathcal {B}_{k, t} \) formed in FIG using \textbf{hot word graph} \(\mathcal {G}_{k, t} = (\mathcal{B}_{k, t}, \mathcal{E}_{k, t}) \) indicates,
\(\mathcal{E}_{k, t} = \{(a, b) | a \in \mathcal{B}_{k, t}, b \in \mathcal {B} _ {k, t }, PMI (\mathcal{D}_{k, t}, a, b)> 0 \} \), where \(PMI (\mathcal{D}_{k, t}, a, b) \) the field \(k \) time window \(t \) related microblog \(\ mathcal {D} _ {k, t} \) on the word \(a \) and the word \(b \) point metric information between each other.
% Refer to bursty.py getSimGraph () function

>>>>

\section{Proposed Method}
\subsection{Initialization of Normal States}
\textbf{User profile.} User usually describes herself or himself by a piece of short text on microblog platform.
This short text can be a continuous string or an array of hash tags, e.g., "\textit{Co-founder of Twitter, Medium, and now Co-founder and CEO of Askjelly.com}" of Biz Stone or "\textit{\#Cloud}, \textit{\#YARN}" of @hadoopchina.
Though it's easy to estimate Biz Stone's interests by his self-description text, it's not always capable of doing so because some users' are very short.
To overcome this limitation, we define \textbf{user profile} \(\bm{p_u}\) as combining user \(u\)'s self-description text with the texts provided by \(u\)'s followings. 
Taking Biz Stone as an example, he follows 696 accounts, in which there are 60 founders, 27 CEOs, 21 Google related, and 9 medium related accounts, etc. 
This example demonstrates that user profile \(p_u\) can be augmented by gathering the followings' information.

@@

\begin{equation}
\label{eq:wikiPrior}
\begin{aligned}
\tau_{kv}=
\left\{ \begin{aligned}
W \frac{f_{kv}}{\sum_{v\in S_{kv}}f_{kv}} &,v\in S_{k} \\
0&,v \notin S_{k}\\
\end{aligned}\right.
\end{aligned}
\end{equation}

@@

As shown in Figure \ref{fig: windowsBurstyWordGraph} below, we will one area, a hot word of the time window and hot words between to diagram.
Hot words set \(\ mathcal{B}_{k, t} \) formed in FIG using \textbf{hot word graph} \(\mathcal {G}_{k, t} = (\mathcal{B}_{k, t}, \mathcal{E}_{k, t}) \) indicates,
\(\mathcal{E}_{k, t} = \{(a, b) | a \in \mathcal{B}_{k, t}, b \in \mathcal {B} _ {k, t }, PMI (\mathcal{D}_{k, t}, a, b)> 0 \} \), where \(PMI (\mathcal{D}_{k, t}, a, b) \) the field \(k \) time window \(t \) related microblog \(\ mathcal {D} _ {k, t} \) on the word \(a \) and the word \(b \) point metric information between each other.
% Refer to bursty.py getSimGraph () function
